The \textit{Kepler} Smear Campaign: Light curves for 102 Very Bright Stars

### 2019-05-20 paper/ms.tex
lucey orcid
update
figures and tables amended
figures
final version?
typo

\author{Madeline Lucey}
\affiliation{Department of Astronomy, The University of Texas at Austin, 2515 Speedway Boulevard, Austin, TX 78712, USA}

@@

% \begin{figure}
% \noindent\includegraphics[width=8cm,keepaspectratio]{venn.png}
% \caption{\label{venn}
% Venn diagram showing the overall structure of the \kepler Smear Campaign sample, showing the subsets for which TRES spectroscopy and asteroseismology are available and their overlap.}
% \end{figure}

@@

\begin{figure}
\plotone{contam.eps}

\caption{\label{contamination2}
Histogram over overlap integrals of smoothed periodograms of odd and even quarters for each star in the sample. The peak at $\sim 0.91$ contains normal stars with limited contamination; we investigate the 22 stars with overlaps below 0.9 for which there is a significant possibility of contamination.}
\end{figure}

@@

\begin{figure}
% \noindent\includegraphics[width=17cm,keepaspectratio]{different_constraints_fullsample_ove02.pdf}
\plotone{different_constraints_ben.pdf}

\caption{\label{masses}
Using asteroseismic constraints only (red) and asteroseismic and spectroscopic constraints jointly (blue) we infer the masses of each star in the asteroseismic sample of giants.}
\end{figure}

\begin{figure}
\plotone{combined_radii.eps}

@@

In Fig.~\ref{alphael}, we display the [Mg/Fe] abundance ratio as a function of [Fe/H] for our stars (black circles), compared\footnote{There may to be systematics between our [X/Fe] abundance scale and those of our comparison samples.} to representative thick and thin disk stars from \cite[open red squares]{Bensby2014} and \cite[open blue triangles]{Adibekyan2012}.

@@

\begin{figure*}
\plotone{HD_183124.png}

\caption{\label{HD_183124}
Power spectrum (left) and period \'{e}chelle diagram (right) of the solar-like oscillations of the red clump star HD~183124. The modes in the power spectrum used for the period \'{e}chelle diagram are highlighted with blue dots. In the period \'{e}chelle diagram we see the characteristic pattern of `bumped' modes from avoided crossings between the comb of \textit{p}-modes and \textit{g}-mode oscillations with a period spacing of $\Delta \Pi = 300.1~\text{s}$.}
\end{figure*}

@@

In four of the five targets we found evidence for binarity, while in the fifth (HD\,185397) there was some time-delay variation but there was no agreement between different modes so it is not of binary origin. Of the others, HD\,175841 and HD\,177781 are probably very long-period binaries, with periods far exceeding the Kepler datasets of $\sim$1470\,d. HD\,181521 appears to be an eccentric binary with a period of at least 1000\,d, but there is only 1 maximum and 1 minimum in the time-delay curve \citep[cf.][]{murphy&shibahashi2015}, so a unique orbital solution was unobtainable. Finally, HD\,186255 is probably a binary with a period of $\sim$415\,d (Figure~\ref{pm}), but there is a slight aperiodicity in the time delays, likely caused by beating between pulsation modes that are not well-separated in the frequency. That, coupled with the fact that this star falls on the failed Module 3 and is therefore missing data every 4th quarter (i.e. $\sim$93 of every 372.5\,d), makes the binary classification uncertain. If this is indeed a 415-d binary, the time delays are consistent with a companion of minimum mass $\sim$0.45\,M$_{\odot}$ in an orbit of moderate eccentricity ($\sim$0.15).

\begin{figure*}
\plotone{HD186255_time-delay_plot.png}

\caption{\label{pm}
Time delay as a function of time for the $\delta$\,Sct star HD~186255, calculated for three of its oscillation modes ($f_2$, $f_5$, and $f_8$) and their average. These vary in unison, but with a small amplitude, and are possibly indicative of a low-mass or highly inclined companion.}
\end{figure*}

>>>>

\author[0000-0001-7297-8508]{Madeline Lucey}
\affiliation{Department of Astronomy, The University of Texas at Austin, 2515 Speedway Boulevard, Austin, TX 78712, USA}

@@

@@

\begin{figure}
\plotone{contam.pdf}
\caption{\label{contamination2}
Histogram over overlap integrals of smoothed periodograms of odd and even quarters for each star in the sample. The peak at $\sim 0.91$ contains normal stars with limited contamination; we investigate the 22 stars with overlaps below 0.9 for which there is a significant possibility of contamination.}
\end{figure}

@@

\begin{figure}
\plotone{different_constraints_ben.pdf}
\caption{\label{masses}
Using asteroseismic constraints only (red) and asteroseismic and spectroscopic constraints jointly (blue) we infer the masses of each star in the asteroseismic sample of giants.}
\end{figure}

\begin{figure}
\plotone{combined_radii.pdf}

@@

In Fig.~\ref{alphael}, we display the [Mg/Fe] abundance ratio as a function of [Fe/H] for our stars (black circles), compared\footnote{There may be systematics between our [X/Fe] abundance scale and those of our comparison samples.} to representative thick and thin disk stars from \cite[open red squares]{Bensby2014} and \cite[open blue triangles]{Adibekyan2012}.

@@

\begin{figure*}
\plotone{HD_183124.pdf}
\caption{\label{HD_183124}
Power spectrum (left) and period \'{e}chelle diagram (right) of the solar-like oscillations of the red clump star HD~183124. The modes in the power spectrum used for the period \'{e}chelle diagram are highlighted with blue dots. In the period \'{e}chelle diagram we see the characteristic pattern of `bumped' modes from avoided crossings between the comb of \textit{p}-modes and \textit{g}-mode oscillations with a period spacing of $\Delta \Pi = 300.1~\text{s}$.}
\end{figure*}

@@

In four of the five targets we found evidence for binarity, while in the fifth (HD\,185397) there was some time-delay variation but there was no agreement between different modes so it is not of binary origin. Of the others, HD\,175841 and HD\,177781 are probably very long-period binaries, with periods far exceeding the Kepler datasets of $\sim$1470\,d. HD\,181521 appears to be an eccentric binary with a period of at least 1000\,d, but there is only 1 maximum and 1 minimum in the time-delay curve \citep[cf.][]{murphy&shibahashi2015}, so a unique orbital solution was unobtainable. Finally, HD\,186255 is probably a binary with a period of $\sim$415\,d (Figure~\ref{pm}), but there is a slight aperiodicity in the time delays, likely caused by beating between pulsation modes that are not well-separated in the frequency. That, coupled with the fact that this star falls on the failed Module~3 and is therefore missing data every 4th quarter (i.e. $\sim$93 of every 372.5\,d), makes the binary classification uncertain. If this is indeed a 415-d binary, the time delays are consistent with a companion of minimum mass $\sim$0.45\,M$_{\odot}$ in an orbit of moderate eccentricity ($\sim$0.15).

\begin{figure*}
\plotone{HD186255_time_delay.pdf}
\caption{\label{pm}
Time delay as a function of time for the $\delta$\,Sct star HD~186255, calculated for three of its oscillation modes ($f_2$, $f_5$, and $f_8$) and their average. These vary in unison, but with a small amplitude, and are possibly indicative of a low-mass or highly inclined companion.}
\end{figure*}
